hormones

### 2020-01-14 analysis/07_hormones.Rmd
new correlations

```{r cort}
p1 <- hormones %>%
  filter(hormone == "cort",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Corticosterone" , x = NULL) +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(0,8.5))
p1

@@

p12 <- plot_grid(p1,p2, rel_widths = c(0.2,0.8))

@@

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4))

@@

```{r PRL}
p1 <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Prolactin" , x = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) 
p1

@@

>>>>

```{r cort}

hormones %>%
  filter(hormone == "cort") %>%
  group_by(sex) %>%
  summarise(mean = mean(plasma_conc),
            median = median(plasma_conc))

p1 <- hormones %>%
  filter(hormone == "cort",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Corticosterone" , x = NULL) +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(0,8.5))
p1

@@

p12 <- plot_grid(p1,p2, rel_widths = c(0.2,0.8), labels = c("a","b"), label_size = 8)

@@

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4), labels = c("c","d"), label_size = 8 )

@@

```{r PRL}
hormones %>%
  filter(hormone == "prolactin") %>%
  group_by(sex) %>%
  summarise(m = mean(plasma_conc),
            median = median(plasma_conc))

p1 <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Prolactin" , x = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) 
p1

@@

```{r correlations2 }
hormoneswide <- hormones %>%
  select(study, treatment, sex, bird_id, hormone, plasma_conc) %>%
  pivot_wider( names_from = hormone, values_from  = plasma_conc, values_fn = list(plasma_conc = mean))

plotcorrelations <- function(i,j, myxlab, mylab, mysubtitle){
      p <- ggplot(hormoneswide, aes(x = i, y = j),na.rm = TRUE) +
       geom_point(aes(color = treatment), na.rm = TRUE) +
       geom_smooth( method = lm, color = "darkgrey", na.rm = TRUE ) +
       theme_B3() +
      #facet_wrap(~sex, scales = "free") +
        labs(x = myxlab, y = mylab, subtitle = mysubtitle) +
        theme(legend.position = "none")

      return(p)
  }

p1 <- plotcorrelations(hormoneswide$prolactin, hormoneswide$cort, "prolactin", "cort", "r = 0.221, p = 0.001")
p2 <- plotcorrelations(hormoneswide$prolactin, hormoneswide$progesterone, "prolactin", "progesterone", "r = -0.099, p = 0.2")
p3 <- plotcorrelations(hormoneswide$prolactin, hormoneswide$testosterone, "prolactin", "testosterone", "r = -0.258, p = 0.08")
p4 <- plotcorrelations(hormoneswide$prolactin, hormoneswide$estradiol, "prolactin", "estradiol", "r = 0.05, p = 0.6")

p5 <- plotcorrelations(hormoneswide$cort, hormoneswide$progesterone, "cort", "progesterone", "r = 0.104, p = 0.175")
p6 <- plotcorrelations(hormoneswide$cort, hormoneswide$estradiol, "cort", "estradiol", "r = -0.026, p = 0.8")
p7 <- plotcorrelations(hormoneswide$cort, hormoneswide$testosterone, "cort", "testosterone", "r = -0.108, p = 0.4")

p8 <- plotcorrelations(hormoneswide$progesterone, hormoneswide$estradiol, "progesterone", "estradiol", "r = 0.120, p = 0.3")
p9 <- plotcorrelations(hormoneswide$progesterone, hormoneswide$testosterone, "progesterone", "testosterone", "r = 0.133, p = 0.3")

allcorrs <- plot_grid(p1,p2,p3,p4,p5,p6,p7,p8,p9, nrow = 3, align = "hv", labels = "auto", label_size = 8)
allcorrs

plot_grid(p1,p3 + theme(legend.position = "right"), align = "hv", rel_widths = c(0.4,0.6))

cor.test(hormoneswide$prolactin, hormoneswide$cort)
cor.test(hormoneswide$prolactin, hormoneswide$progesterone)
cor.test(hormoneswide$prolactin, hormoneswide$estradiol)
cor.test(hormoneswide$prolactin, hormoneswide$testosterone)

cor.test(hormoneswide$cort, hormoneswide$estradiol)
cor.test(hormoneswide$cort, hormoneswide$testosterone)
cor.test(hormoneswide$cort, hormoneswide$progesterone)

cor.test(hormoneswide$progesterone, hormoneswide$estradiol)
cor.test(hormoneswide$progesterone, hormoneswide$testosterone)
```
